Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-04 programlogic.tex
+

\textsf{vProp } \Sigma \; : \; \textsf{bi} \; \stackrel{def}{=} \mathcal{W}_{64} -\textsf{b}> \textsf{iPropI } \Sigma

@@

We abstract memory addresses and registers naming their relevant values through well-known separation logic assertion \textit{points-to}.

@@

\paragraph{Physical-Memory points-to} Our physical memory points-to relation ($\pfpointsto\locsf\locsf\qfrac\ppts$) exhibits nested-mappings abstracting the  masks applied on the indexing virtual address ($\textsf{vaddr}\in\mathcal{W}_{64}$). The unfolded definition of the physical mapsto 

@@

where, for an example virtual address \textsf{va} and given \textsf{CR3} in Figure \ref{}, we can abstract the L4-L1 table traversal as the following:

>>>>

\textsf{vProp } \Sigma \; : \; \textsf{bi} \; \stackrel{def}{=} \mathcal{W}_{64} \rightarrow_{\textsf{b}} \textsf{iPropI } \Sigma

@@

We abstract physical memory addressing and registers naming with well-known separation logic assertion \textit{points-to} assertions.

@@

\paragraph{Physical-Memory points-to} Our physical memory points-to relation for a page table entry (e.g. \textsf{PDE} in Figure \ref{fig:physicalpointsto}) abstracts masking -- $|^{52}$ for frame for and $|^{12}$ for offset -- through logical nested maps.  

@@

Given the definition of physical page-pointsto assertion and the root address of virtual-address space kept in the control register \textsf{CR3} as shown in Figure \ref{fig:pagetable},  one can build the physical address-translation for a virtual address (e.g. \textsf{va}) via abstracting the L4-L1 table traversal as the following:
